Selective electroporation of the viral envelope via optimal control of transmembrane potential

### 2021-06-26 documents/pure_electroporation.tex
Working on Nagurka

An advantage of bang-bang or bang-off-bang over is that the values of u0 are not free. In this case, it was often found that (perhaps due to poorly-chosen values of the penalty factor rho, a poor initial guess, or some other issue in the problem setup), the gradient descent would decrease the control magnitude to a value below numerical accuracy. This necessitated a Lagrange constraint on the total, further increasing the computational complexity and restricting the class of solutions.

@@

@@

\subsection*{Bang-bang control}

@@

@@

optimal over a distribution

@@

>>>>

mayer (endpoint) or Lagrange (integral)

An advantage of bang-bang or bang-singular-bang over is that the values of u0 are not free. In PSOPT and , it was often found that (perhaps due to poorly-chosen values of the penalty factor rho, a poor initial guess, or some other issue in the problem setup), the gradient descent would decrease the control magnitude to a value below numerical accuracy. This necessitated a Lagrange constraint on the integral, further increasing the computational complexity and restricting the class of solutions.

@@

\subsection*{Hampath bang-bang control}

@@

\subsection*{Niemann's bang-bang control control}

Niemann describes a straightforward bang-bang formulation using gradient methods, using gradient projection to implement the required boundaries \cite{Determinationa}. Because the unit step function of the transmembrane voltage is analytic, a bang-bang control can be simulated without integration, by simply summing the (as described by Kotnik). This appears to automatically resolve "backwards-integration" and sorting issues presented in chapter 3 of Niemann's thesis.

While

@@

As previously mentioned, electroporation is rarely seen in non-contact studies. It is possible that some nuanced

@@

Viruses vary by \%x . optimal over a distribution of cells and viruses.

@@

must necessarily operate "open loop", without feedback, towards the transmembrane voltage
